The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/methods.tex
63 pass

\dave{Ty: a bit more here, show the transformation of the integral via divergence theorem then show the final discrete version. Clearly define the quadrature rules.}
The key idea behind raycasting quadrature is to transform a domain integral of the form $I=\int_{\Omega} f(X,Y,Z) d\Omega$ to an easier form that enables us to select quadrature points in an entirely meshless manner. The first transformation is to convert the domain of the integral to an \textit{auxiliary domain}, $\Omega_R$ on which integration is easy to compute. In our case we take this domain to be an axis-aligned bounding box around our model, and rewrite integration as $I=\int_{\Omega_R} g(X,Y,Z) d\Omega_R$ where $g$ evaluates to zero outside of $\Omega$, but equals $f$ inside $\Omega$. Next we apply the Divergence theorem \ty{the paper calls it Green-Gauss theorem, but these are same, right} to rewrite our integral as
\newcommand{\Zeta}{\mathrm{Z}}
\begin{equation}
\int_{\Omega_R} g(X,Y,Z) d\Omega_R = \int_{\Gamma_R}\left(\int_{X_1}^{X_2} g(\alpha, Y, Z) d\alpha)\right)\mathbf{n} d\Gamma.
\end{equation}
where $\Gamma_R$ is the boundary of the bounding box with normals $\mathbf{n}$ and $X_1$ and $X_2$ represent the minimum and maximum values of the box along the $x$-axis. With this form, all we require to evaluate the outer integral is to integrate over the $y$-$z$ plane located at $X_1$. With this simple form, the normal term may be excluded as it always equals $1$ in the case of an axis-aligned bounding box. Finally, raycasting is used to evaluate the line integral along the x-axis. From here, we find all the intersection intervals where the ray is inside $\Omega$, and select quadrature points uniformly along this interval. Thus, this transformation from the original volume integral two and integral over a $y$-$z$ plane plus axis-aligned rays enables us to integrate the volumes of our NURBS models in a completely meshless approach.

We make a minor modification this procedure to handle common geometric pathologies encountered in NURBS modelling, such as overlapping surfaces by performing 
CSG unions while raycasting~\cite{ROTH1982109}. 
The output of this raycasting procedure is a set of quadrature points $\st{X}$ and weights $\st{v}$ that we use for integration and also as input to our 
deformation origin extraction~\refsec{origins} and blending weights computation~\refsec{weights}
\reffig{raycasting} shows the convergence of this quadrature approach when used to compute the volume of a NURBS model.
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/raycasting_quadrature}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}

@@

\begin{algorithm}[h]
	\begin{algorithmic}[1]
		\Procedure{Preprocess}{$model$}
     	\myworries{todo: add volume}
     	\While {$simulating$}
     		\State{$\Pcox \gets \Pi\mathbf{q}$}
     		\ForAll{$i \gets 1$ to $|\st{X}|$}
     			\State{$\mathbf{F}_i \gets \frac{\partial \mathbf{F}}{\partial c} c$}
				\State{$\frac{\partial V}{\partial c} \gets \frac{\partial V}{\partial c} +
				\frac{\partial \mathbf{F}}{\partial c}^T \frac{\partial \psi}{\partial \mathbf{F}}(\mathbf{F}_i)$}

				\State{$\frac{\partial^2 V}{\partial c^2} \gets \frac{\partial^2 V}{\partial c^2} +
				 \frac{\partial \mathbf{F}}{\partial c}^T 
				 \frac{\partial^2 \psi}{\partial \mathbf{F}^2}(\mathbf{F}_i)
				 \frac{\partial \mathbf{F}}{\partial c}
				 $}
  			\EndFor
  			\State{$K \gets \Pi^T \frac{\partial^2 V}{\partial c^2} \Pi$}
  			\State{$f_{\text{internal}} \gets \Pi^T \frac{\partial V}{\partial c}$}
  			\State{$f_{\text{error}} \gets \ME \vc{q}$}
  			\State{$f_{\text{total}} \gets f_{\text{internal}} + f_{\text{error}} + f_{\text{ext}}$}
  			\State{$\dot{\mathbf{q}} \gets \text{TimeIntegration}
  			(f_{\text{total}},\mathbf{K}, \dot{\mathbf{q}}, \mathbf{J} , \mathbf{M}, \mathbf{M_E})$}
  			\State{$\mathbf{q} \gets \mathbf{q} + h\dot{\mathbf{q}}$}
     	\EndWhile
	\EndProcedure
\end{algorithmic}
\caption{Shape Matching Element Simulation Loop}
\label{alg:sem_simulation}
\end{algorithm}

>>>>

\dave{Ty: a bit more here, show the transformation of the integral via divergence theorem then show the final discrete version. Clearly define the quadrature rules.}
The key idea behind raycasting quadrature is to transform a domain integral of the form $I=\int_{\Omega} f(X,Y,Z) d\Omega$ to an easier form that enables us to select quadrature points in an entirely meshless manner. The first transformation is to convert the domain of the integral to an \textit{auxiliary domain}, $\Omega_R$ on which integration is easy to compute. In our case we take this domain to be an axis-aligned bounding box around our model, and rewrite integration as $I=\int_{\Omega_R} g(X,Y,Z) d\Omega_R$ where $g$ evaluates to zero outside of $\Omega$, but equals $f$ inside $\Omega$. Next we apply the Divergence theorem to rewrite our integral as
\newcommand{\Zeta}{\mathrm{Z}}
\begin{equation}
\int_{\Omega_R} g(X,Y,Z) d\Omega_R = \int_{\Gamma_R}\left(\int_{X_1}^{X_2} g(\alpha, Y, Z) d\alpha)\right)\mathbf{n} d\Gamma.
\end{equation}
where $\Gamma_R$ is the boundary of the bounding box with normals $\mathbf{n}$ and $X_1$ and $X_2$ represent the minimum and maximum values of the box along the $x$-axis. With this form, all we require to evaluate the outer integral is to integrate over the $y$-$z$ plane located at $X_1$. With this simple form, the normal term may be excluded as it always equals $1$ \dave{isn;t it a vector $(1,0,0)$ or something like that ? }in the case of an axis-aligned bounding box. Finally, raycasting is used to evaluate the line integral along the x-axis. From here, we find all the intersection intervals where the ray is inside $\Omega$, and select quadrature points uniformly along this interval. Thus, this transformation from the original volume integral two and integral over a $y$-$z$ plane plus axis-aligned rays enables us to integrate the volumes of our NURBS models in a completely meshless approach.

We make a minor modification this procedure to handle common geometric pathologies encountered in NURBS modelling, such as overlapping surfaces by performing 
CSG unions while raycasting~\cite{ROTH1982109}. 
The output of this raycasting procedure is a set of quadrature points $\st{X}$ and weights $\st{v}$ that we use for integration and also as input to our 
deformation origin extraction~\refsec{origins} and blending weights computation~\refsec{weights}
\reffig{raycasting} shows the convergence of this quadrature approach when used to compute the volume of a NURBS model. 
In principle we could apply detail-aware sampling methods~\cite{DBLP:journals/tog/WangFP12} to improve the robustness of raycasting quadrature even further,
but we found it unnecessary for the examples in this paper.
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/raycasting_quadrature}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}

@@

\begin{algorithm}[h]
	\begin{algorithmic}[1]
		\Procedure{Simulate}{$model$}
     	 %\MM\ddot{\vc{q}} = \fo\left(\vc{q}\right) + \vc{f}_g + \fext,
     	\While {$simulating$}
     		\State{$\Pcox \gets \Pi\vc{q}$}
     		\ForAll{$i \gets 1$ to $|\st{X}|$}
     			\State{$\mathbf{F}_i \gets \frac{\partial \mathbf{F}}{\partial c} c \quad$ // deformation gradient}
				\State{$\frac{\partial V}{\partial c} \gets \frac{\partial V}{\partial c} +
				\frac{\partial \mathbf{F}}{\partial c}^T \frac{\partial \psi}{\partial \mathbf{F}}(\mathbf{F}_i) \cdot \text{volume}_i$}

				\State{$\frac{\partial^2 V}{\partial c^2} \gets \frac{\partial^2 V}{\partial c^2} +
				 \frac{\partial \mathbf{F}}{\partial c}^T 
				 \frac{\partial^2 \psi}{\partial \mathbf{F}^2}(\mathbf{F}_i) 
				 \frac{\partial \mathbf{F}}{\partial c}
				 \cdot \text{volume}_i$}
  			\EndFor
  			\State{$K \gets \Pi^T \frac{\partial^2 V}{\partial c^2} \Pi$}
  			\State{$\fo\left(\vc{q}\right) \gets \Pi^T \frac{\partial V}{\partial c} + \ME \vc{q}$}
  			\State{$\vc{f}_{\text{total}} \gets \fo\left(\vc{q}\right) + \vc{f}_g + \fext$}
  			\State{$\dot{\vc{q}} \gets \text{TimeIntegration}
  			(K, \vc{f}_{\text{total}}, \dot{\vc{q}}, \samp{\Jnurbs} , \MM, \ME)$}
  			\State{$\vc{q} \gets \vc{q} + h\dot{\vc{q}} \quad$ // $h$ is timestep size}
     	\EndWhile
	\EndProcedure
\end{algorithmic}
\caption{Shape Matching Element Simulation Loop}
\label{alg:sem_simulation}
\end{algorithm}
